Global Optimization of an Analog Method by Means of Genetic Algorithms

### 2016-09-02 Genetic algorithms - MWR/template.tex
GAs paper under correction.

We will begin by presenting the basics of the considered AM variants (section \ref{sec:method_data}) and the assessed GAs options (section \ref{sec:gas}). The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.

@@

AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:method_data}.\ref{sec:data}). Based on these analogue observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.

@@

In the present study, the choice of the meteorological variables considered as predictors is still set a priori. Then, for every level of analogy, GAs have to optimize jointly (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case). The first experiments are on a single level of analogy (on the geopotential height, see section \ref{sec:method_data}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.

@@

The first analysis was the optimization of the precipitation downscaling over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig. \ref{fig:operator_mutation_score_atmlevel}). The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy). The resulting CRPSS performance score (section \ref{sec:method_data}.\ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig. \ref{fig:operator_mutation_score_atmlevel}). For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line). A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}. This application however demonstrates that, when correctly configured, GAs can automatically and successfully choose the pressure levels. However, some less relevant optimizations do not match the previous results. Through different applications, the automatic selection of the pressure level was shown to significantly increase the difficulty for GAs to converge to a unique solution, ideally the global optimum. A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient. However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM considered.

>>>>

The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}). The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.

@@

AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}.\ref{sec:data}). Based on these analogue observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.

@@

In the present study, the choice of the meteorological variables considered as predictors is still set a priori. Then, for every level of analogy, GAs have to optimize jointly (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case). The first experiments are on a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.

@@

The first analysis was the optimization of the precipitation downscaling over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig. \ref{fig:operator_mutation_score_atmlevel}). The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy). The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig. \ref{fig:operator_mutation_score_atmlevel}). For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line). A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}. This application however demonstrates that, when correctly configured, GAs can automatically and successfully choose the pressure levels. However, some less relevant optimizations do not match the previous results. Through different applications, the automatic selection of the pressure level was shown to significantly increase the difficulty for GAs to converge to a unique solution, ideally the global optimum. A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient. However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM considered.
